Evaluating Informative Hypotheses with Equality and Inequality Constraints:~A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2021-11-28 Documents/Bookdown/index.Rmd
fix title supplemental

--- 
title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Supplemental Material of the article “Evaluating informative hypotheses with equality and inequality constraint: A tutorial using the Bayes factor via the encompassing prior approach”"
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

>>>>

--- 
title: "Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Supplemental Material of the article “Evaluating informative hypotheses with equality and inequality constraint: A tutorial using the Bayes factor via the encompassing prior approach”"
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

### 2021-11-28 docs/attachment-bayes-factor.tex
fix title supplemental

  pdftitle={Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach},

@@

\title{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplemental Material}
\author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
\date{2021-11-28}

>>>>

  pdftitle={Evaluating Informative Hypotheses with Equality and Inequality Constraints:~A Tutorial Using the Bayes Factor via the Encompassing Prior Approach},

@@

\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints:~A Tutorial Using the Bayes Factor via the Encompassing Prior Approach}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplemental Material}
\author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
\date{2021-11-28}
